---
title: "Covid91 vaccine study Final2023"
author: "Put your name here!"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

$H_0$ The COVID vaccine has no effect on people in different subgroups.


$H_A$ The COVID vaccine does have an effect in different subgroups.

## Methods 

This statistical analysis we will be using is catergorical ~ categorical, because the COVID vaccine should be effective among subgroups

The method we will be using to display the data us a bar chart, cross table, and chisquaar test

## Males

## Results

```{r}
maleData = filter (FinalData,sex == "M")
```

## Descriptive Results

### Graphical Descriptive 

```{r}
barchartGC(~infected+treatment,data=maleData)
barchartGC(~infected+treatment,data=maleData, type="percent")

```

Based on the graph, it is showing us that the group of people who contracted COVID and the ones who received the vaccine had less symptoms than those that received the placebo, while the all male group that didn't contract COVID showed no difference between those who were vaccinated and unvaccinated. 

### Numerical Descriptive

```{r}
table1 <- xtabs(~infected + treatment, data=maleData)
rowPerc(table1)
colPerc(table1)
```

The table shows that the group with COVID experience a 2x difference between the vaccinated and the un-vaccinated.The placebo group had around a 70% infected rate compared to the vaccinated group which only had about 30%. The Ok group had no significant difference between the un-vaccinated and vaccinated

### Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


The p-value is 0.0000001098, concluding that the p value is so small that we are rejecting the null hypothesis. Showing that COVID vaccine is effective between the male subgroup.

Based on the Fisher exact test value, you become .35% more susceptible to contracting COVID if you are unvaccinated. 

## Females

## Results

```{r}
femaleData = filter (FinalData,sex == "F")
```

## Descriptive Results

### Graphical Descriptive 

```{r}
barchartGC(~infected+treatment,data=femaleData)
barchartGC(~infected+treatment,data=femaleData, type="percent")
```

This graph is showing that from the all female group who contracted COVID, the ones who received the vaccine had less symptoms than those with the placebo while the all the female group that did not contract COVID showed no difference between those who were vaccinated and not vaccinated. 

### Numerical Descriptive

```{r}
table2 <- xtabs(~infected + treatment, data=femaleData)
rowPerc(table2)
colPerc(table2)
```

This table shows that within the all female group those who weren't vaccinated had a 60% infection rate while those who were vaccinated had a 40% infection rate.

In the all female group that contracted COVID those with the vaccine had .67% less symptoms compared to those who weren't vaccinated.

## Inferential Results

```{r}
chisq.test(table2)
chisqtestGC(table2)
fisher.test(table2)
```

Based on this chisq test, the p-value is 0.0002732, showing that there is a significant difference, concluding that we are failing to reject the null hypothesis. This means that the COVID vaccine is ineffective within the female subgroup. 

## LGBTQ

## Results

```{r}
LGBTQData = filter (FinalData,LGBTQ == "gay")
```

## Descriptive Results

### Graphical Descriptive 

```{r}
barchartGC(~infected+treatment,data=LGBTQData)
barchartGC(~infected+treatment,data=LGBTQData, type="percent")

```
This graph is showing that within the LGBTQ subgroup, those who got COVID and got vaccinated experienced significantly more symptoms than those their unvaccinated counterpart. Those who did not get COVID and were both vaccinated and unvaccinated did not show any difference.


### Numerical Descriptive

```{r}
table3 <- xtabs(~infected + treatment, data=LGBTQData)
rowPerc(table3)
colPerc(table3)
```
This table is showing that within the LGBTQ group, those who were not vaccinated had a 15.38% infection rate while those who were not vaccinated had a 84.62 infection rate.

In the all LGBTQ group that contracted COVID, those with the vaccine had 2.8x more symptoms than those who were not vaccinated.

## Inferential Results

```{r}
chisq.test(table3)
chisqtestGC(table3)
fisher.test(table3)
```



# Discussion and Conclusion


## Druggies

## Results

```{r}
DruggiesData = filter(FinalData, DrugUser == "yes")
```

## Descriptive Results

### Graphical Descriptive 

```{r}
barchartGC(~infected+treatment,data=DruggiesData)
barchartGC(~infected+treatment,data=DruggiesData, type="percent")

```

This graph us showing that from the drug user group who contracted COVID, the ones who received the vaccine had more symptoms than those with the placebo while drug user group that did not contract COVID showed no difference between those who were vaccinated and not vaccinated.

### Numerical Descriptive

```{r}
table4 <- xtabs(~infected + treatment, data=DruggiesData)
rowPerc(table4)
colPerc(table4)
```


## Inferential Results

```{r}
chisq.test(table4)
chisqtestGC(table4)
fisher.test(table4)
```

Based on this chisq test, the p-value is 0.0000002842 concluding that the there is a 

Based on this chisq test, the p-value is 0.0002732, showing that there is a significant differecne, concluding that we are failing to reject the null hypothesis. This means that the COVID vaccine is ineffective within the female subgroup. 


# Discussion and Conclusion


# Overall Results and Conclusions